Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
ASSR: write results for MFCCs

%For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results. \ja{Why?}

>>>>

The same observations are made for the MFCCs for a $k\leq5$. However for a rank $k$ greater than 5, there is no clear evidence that \emph{ob-c} and \emph{ob-w} approaches improve the results compared to \emph{early}. The latter even outperform \emph{ob-a} for $k\geq5$.

From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This is may due to the fact that, at some point, the MFCCs fail to capture the discriminant information contained in the larger-scale modulations, thus making a centroids-based description useless, or even counterproductive when the centroids are not weighted.
